Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-10-27 analysis/paper/paper.qmd
made plots for only LGM artifacts

korean_archaeological_site_locations_tcsa <- 
  tcsa %>% 
  mutate(Site_name_to_join = str_squish(Site_name)) %>% 
  left_join(korean_archaeological_site_locations %>% 
              mutate(Site_name_to_join  = str_squish(Site_name)),
                     by = "Site_name_to_join") %>% 
  drop_na(min_tcsa)

ggmap(map)  +
  geom_jitter(data = korean_archaeological_site_locations_tcsa,
             aes(long_dd ,
                 lat_dd,
                 colour = min_tcsa),
             size = 3,
             width = 0.25, 
             height = 0.25) +
  scale_color_viridis_c(option = "A") +
  theme_minimal(base_size = 6) +
  labs(x = "Longitute",
       y = "Latitude") +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank())

@@

# Convert to class 'sf'
pts <- st_as_sf(korean_archaeological_site_locations_tcsa,
                coords = c(   "long_dd", "lat_dd"),
                crs = st_crs(veg))

@@

ggplot() +
  geom_sf(data = veg) +
  geom_sf(data = pts)

>>>>

korean_archaeological_site_locations_tcsa <- 
  tcsa %>% 
  left_join(mydata_ages) %>% # add age data
  group_by(Assemblage) %>% 
  mutate(Site_name_to_join = str_squish(Site_name)) %>% 
  left_join(korean_archaeological_site_locations %>% 
              mutate(Site_name_to_join  = str_squish(Site_name)), # deleted invisible space in the data set probably created during data collecting
                     by = "Site_name_to_join") %>% 
  drop_na(min_tcsa) %>% 
  drop_na(age)

# data only for LGM period
tcsa_lgm <- korean_archaeological_site_locations_tcsa %>% 
  filter(age< 26.5 & age> 19)

ggmap(map)  +
  geom_jitter(data = tcsa_lgm,
             aes(long_dd.y ,
                 lat_dd.y,
                 colour = min_tcsa),
             size = 3,
             width = 0.25, 
             height = 0.25) +
  scale_color_viridis_c(option = "A") +
  theme_minimal(base_size = 6) +
  labs(x = "Longitute",
       y = "Latitude") +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank())

@@

# Convert to class 'sf'
pts <- st_as_sf(tcsa_lgm,
                coords = c(   "long_dd.y", "lat_dd.y"),
                crs = st_crs(veg))

@@

ggplot() +
  geom_sf(data = veg, fill=c("#CCCCCC", "#FFFFFF", "#999999", "#666666")) + #add color for vegetation polygons
  geom_sf(data = pts)
